%
% -----------------------------------------------------------------------------
%
% A license is hereby granted to reproduce this software source code and
% to create executable versions from this source code for personal,
% non-commercial use.  The copyright notice included with the software
% must be maintained in all copies produced.
%
% THIS PROGRAM IS PROVIDED "AS IS". THE AUTHOR PROVIDES NO WARRANTIES
% WHATSOEVER, EXPRESSED OR IMPLIED, INCLUDING WARRANTIES OF
% MERCHANTABILITY, TITLE, OR FITNESS FOR ANY PARTICULAR PURPOSE.  THE
% AUTHOR DOES NOT WARRANT THAT USE OF THIS PROGRAM DOES NOT INFRINGE THE
% INTELLECTUAL PROPERTY RIGHTS OF ANY THIRD PARTY IN ANY COUNTRY.
%
% Copyright (c) 1994-2006, John Conover, All Rights Reserved.
%
% Comments and/or bug reports should be addressed to:
%
%     john@email.johncon.com (John Conover)
%
% -----------------------------------------------------------------------------
%
% Revision: \RCSRevision \\
% Revision Time: \RCSTime UMT \\
% Revision Date: \RCSDate \\
% Revision Id: \RCSId \\
% Revision File: \RCSLog \\
\RCS $Revision: 0.0 $
\RCS $Date: 2006/01/20 04:38:13 $
\RCS $Id: colophon.tex,v 0.0 2006/01/20 04:38:13 john Exp $
% $Log: colophon.tex,v $
% Revision 0.0  2006/01/20 04:38:13  john
% Initial version
%
%
\chapter*{Colophon}
\pagestyle{empty}

    This manuscript was composed using {\TeX}, with the {\LaTeX}
    definitions, and set in the Computer Modern and Postscript
    fonts. For technical information on {\LaTeX}, see {\it {\LaTeX}
    User's Guide \& Reference Manual}, by Leslie Lamport,
    Addison---Wesley Publishing Company, Reading, Massachusetts,
    1986. For technical information on {\TeX}, see {\it The \TeX
    book}\/, by Donald Knuth, Addison---Wesley, Publishing Company,
    Reading, Massachusetts, 1984. {\TeX} is a trademark of The
    American Mathematical Society. The sources to {\TeX} and {\LaTeX}
    are freely available by anonymous ftp to ftp.shsu.edu, in the
    directory pub/tex.

    The editor used in the composition of this manuscript was {\it GNU
    Emacs}\/, with the {\it Auc---Tex}\/ definitions. The sources to
    {\it GNU Emacs}\/ are freely available by anonymous ftp to
    prep.ai.mit.edu in the directory pub/gnu. The sources to {\it
    Auc---Tex}\/ are freely available by anonymous ftp to
    ftp.iesd.auc.dk in the directory pub/TeX/LaTeX.

    The bibliographic database for this manuscript was maintained by
    {\it BibTeX}\/. The sources to {\it BibTeX}\/ are freely available
    by anonymous ftp to ftp.shsu.edu in the directory pub/tex.

    The citations and references were inserted in the manuscript using
    the {\it RefTex}\/ definitions. The {\it RefTex}\/ definitions are
    freely available by anonymous ftp to ftp.shsu.edu in the directory
    pub/tex.

    The page header and footers for the manuscript were defined using
    the {\it fancyheadings}\/ definitions in {\LaTeX}. The sources to
    {\it fancyheadings}\/ are freely available by anonymous ftp to
    ftp.shsu.edu in the directory pub/tex.

    The manuscript's index was made by the program {\it gnuindex}\/.
    The sources to {\it gnuindex}\/ are freely available by anonymous
    ftp to prep.ai.mit.edu in the directory pub/gnu in the {\it
    texinfo}\/ distribution.

    The spelling in the manuscript was verified using {\it ispell}\/
    with {\it GNU Emacs}\/. The sources to {\it ispell}\/ are freely
    available by anonymous ftp to ftp.cs.ucla.edu in the directory
    pub/ispell.

    The portable device output of {\LaTeX} was converted to Postscript
    using the program {\it dvips}\/. The sources to {\it dvips}\/ are
    freely available by anonymous ftp to ftp.shsu.edu in the directory
    pub/tex.

    The graphs in this manuscript were made using the program {\it
    gnuplot}\/. The sources to {\it gnuplot}\/ are freely available by
    anonymous ftp to dartmouth.edu, in the directory pub/gnuplot. The
    graphs were converted to Encapsulated Postscript and imported
    directly into {\LaTeX} using the {\it epsf}\/ definitions. The
    sources to {\it epsf}\/ are freely available by anonymous ftp to
    ftp.shsu.edu in the directory pub/tex.

    The schematic pictographs in this manuscript were made using the
    program {\it xfig}\/. The sources to {\it xfig}\/ are freely
    available by anonymous ftp to ftp.x.org in the directory
    pub/contrib. The Encapsulated Postscript export was done at 25\%
    size, in portrait mode. Many of the pictographs were translated
    from the {\it xfig}\/ file format to Encapsulated Postscript using
    the {\it fig2dev}\/ program that is distributed with the {\it
    xfig}\/ sources.

    The tables in this manuscript were made using the {\it sc}\/
    spreadsheet calculator program. The sources to {\it sc}\/ are
    freely available by anonymous ftp to prep.ai.mit.edu in the
    directory pub/gnu.

    In addition, the document and revision control functionality was
    provided by the program {\it rcs}\/. The sources to {\it rcs}\/
    are freely available by anonymous ftp to prep.ai.mit.edu in the
    directory pub/gnu. The revision control data was imported directly
    into {\LaTeX} using the {\it rcs}\/ definitions. The sources to
    the {\it rcs}\/ definitions are freely available by anonymous ftp
    to ftp.shsu.edu in the directory pub/tex.

    The system used in the composition of this manuscript was {\it
    Linux}\/, version 1.2.8.  The sources to {\it Linux}\/ are freely
    available by anonymous ftp to sunsite.unc.edu in the directory
    pub/Linux. All programs used in composition of this manuscript are
    contained in the ``standard'' {\it Linux}\/ distribution.

% Local Variables:
% TeX-parse-self: t
% TeX-auto-save: t
% TeX-master: "fractal.tex"
% End:
