%
% -----------------------------------------------------------------------------
%
% A license is hereby granted to reproduce this software source code and
% to create executable versions from this source code for personal,
% non-commercial use.  The copyright notice included with the software
% must be maintained in all copies produced.
%
% THIS PROGRAM IS PROVIDED "AS IS". THE AUTHOR PROVIDES NO WARRANTIES
% WHATSOEVER, EXPRESSED OR IMPLIED, INCLUDING WARRANTIES OF
% MERCHANTABILITY, TITLE, OR FITNESS FOR ANY PARTICULAR PURPOSE.  THE
% AUTHOR DOES NOT WARRANT THAT USE OF THIS PROGRAM DOES NOT INFRINGE THE
% INTELLECTUAL PROPERTY RIGHTS OF ANY THIRD PARTY IN ANY COUNTRY.
%
% Copyright (c) 1994-2006, John Conover, All Rights Reserved.
%
% Comments and/or bug reports should be addressed to:
%
%     john@email.johncon.com (John Conover)
%
% -----------------------------------------------------------------------------
%
% Revision: \RCSRevision \\
% Revision Time: \RCSTime UMT \\
% Revision Date: \RCSDate \\
% Revision Id: \RCSId \\
% Revision File: \RCSLog \\
\RCS $Revision: 0.0 $
\RCS $Date: 2006/01/20 04:38:13 $
\RCS $Id: preface.tex,v 0.0 2006/01/20 04:38:13 john Exp $
% $Log: preface.tex,v $
% Revision 0.0  2006/01/20 04:38:13  john
% Initial version
%
%
\chapter*{Preface}
\addcontentsline{toc}{chapter}{Preface}

    This manuscript is a compilation of my un-edited personal notes,
    written over two decades in which I was involved in operational
    management in the electronics industry. One of the issues
    addressed in industrial operations is the dynamics of the market
    place. This manuscript describes an attempt at ``modeling,'' at
    least in a qualitative sense, the dynamics of the North American
    Electronics Industry. Being an engineer by academic tenure, I
    chose fractal methodologies, since a large formal infrastructure
    exists, and it is a ``method of choice,'' where applicable. The
    latter part of my career has been spent in the financial
    community, where such entropic methods have been used,
    controversially, in such areas as ``programmed trading'' in the
    capital markets. The reader should be advised that such methods
    remain controversial, and applications to industrial markets, will
    no doubt, add to the controversy. How applicable the methodology
    is found to be will be left to the reader's discretion.

    Most of the presentation is in chronological order. The
    derivations in chapters~\ref{general} and~\ref{methodology} were
    done over the span of the last decade and a half, and the sections
    are, roughly, in temporal order. The reader should be advised that
    there were paradigm shifts and symbol ambiguities as time
    progressed, and that chapters~\ref{general} and~\ref{methodology}
    are in need of a total rework---they are offered in that context,
    and the reader should be advised that there are, almost
    inevitably, errors in the presentation. (Specifically,
    Section~\ref{samplets} in Chapter~\ref{general} regarding time
    sampled time series should be regarded with scepticism and should
    be used with caution---it is unfortunate that a clear derivation
    of the effect of sampling on time series has not been addressed
    adequately, since there are many issues left open at this time.)

    The programs used in the analysis were written by the author, and
    should be considered as ``fragile,'' since there has never been
    any intention to turn them into ``commercial'' products. They are
    offered in that context, and the reader should be advised that
    there is little or no provision for handling numerical exceptions,
    and no attention given to quality assurance.  The ``C'' language
    sources to the programs are available, as is, by sending an
    electronic mail to john-archive-request@johncon.johncon.com with a
    subject of ``archive get fractal''. The source distribution also
    contains the {\LaTeX} sources to this manuscript.

    The other programs used in the composition of this manuscript are
    all freely available by anonymous ftp. For the list of programs,
    and availability on the Internet, see the colophon.

\def\thismonth % convert numeric month to month name
    {
        \ifcase\month
            \or January\or February\or March\or April\or May\or June
            \or July\or August\or September\or October\or November\or December
        \fi
    }

\begin{flushright}
    ---J. C. C.\\
\end{flushright}

\begin{flushleft}
    \thismonth, \number\year \\
\end{flushleft}

% Local Variables:
% TeX-parse-self: t
% TeX-auto-save: t
% TeX-master: "fractal.tex"
% End:
